\chapter*{ACKNOWLEDGEMENTS}
\addcontentsline{toc}{schapter}{ACKNOWLEDGEMENTS}

I would like to thank to L.A. Adamic, N. Glance, and Gallup for the use of their images in the spirit of academic advancement. Without these resources, my points would both less strong and accessible.

This work would	not	have been possible without the financial support of	California State University, Los Angeles and their generous academic grants and the support of the faculty and staff of the Electrical and Computer Engineering Department. I am especially indebted	to my professors during my time here who have been supportive	of my career goals and who have worked actively to help me to pursue those goals, as well as providing their extensive professional and personal guidance. I would also like to thank my thesis committee members for their input, advice, and interest in this work. 

I am grateful to all of	those with whom I have had the pleasure to work during this	and	other related projects.	I would especially like to thank Dr.~Shaurya Agarwal, the	chairman of	my committee. As my	teacher	and	mentor,	he has taught me more than I could ever give him credit for here. He has shown me, by his example, what a	good researcher, engineer (and person) should be.

Nobody has been	more important to me in	the	pursuit	of this	project	than the members	of	my	family.	I would	like to	thank	my	parents, whose love	and	guidance are with me in	whatever I pursue. They	are	the ultimate role models.	Most importantly, I wish to	thank my loving	and	supportive fiance, Liliane, who has	provided unending understanding, encouragement, and inspiration.